---
title: 'ESM 206 Lab 7: Multiple Linear Regression Intro'
author: "Tommy King"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Installing Packages

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)

```


## Explore Penguins Data Set 

Use `GGally:: ggpairs()` to create a pairs plot. 
```{r}
ggpairs(penguins)

```

That plot is overkill. Lets simplify the variables that we include in our ggpairs plot: 

- species
-bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

```

## Multiple Linear Regression 

We are going to ttry to undersand (a bit better) relationships between multiple predictor variables and an outcome which is penguins body mass. 

The different predictor variable we are going to try are: 

- species
- flipper_length
- sex 
- bill_depth

### Model 1 

Model body mass based on only flipper length and bill depth (bad idea, there are important variables missing).
```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients
model_1

# more information about model and statistics
summary(model_1)
```
If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average. 

Adjusted R-Squared value: 76% of variance in body mass is explained by this model (flipper length and bill depth).

NOTE: Pearson's R depcits correlation of models, versus the R-Squared value depicts the total variance of a dependent variable of a model.

Actually, we think that a model for penguin body mass should contain the variables species, flipper length, and penguin sex. 

### Model 2: 
Penguin body mass based on species, flipper length and sex. 
```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)


# let's look at coefficients
model_2

# Try interpreting the coefficients for flipper length, gentoo, and male. 

#If everything is held constant, we expect that for each 1mm increase in flipper length, there is a 20.02 grams in body mass.


```
We would expect a Gentoo penguin to be, on average, 836.26 grams larger than Adelie penguins if everything else is held constant.

## Visualize this model: 

```{r}
ggplot(data= penguins, 
       aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point(aes(color = species)) + 
  facet_wrap(~ sex)

```

## A couple ways to gert and report multiple Linear regression model outcomes: 

Use broom::tidy() to get model coefficient info in a tidy data frame
```{r}
penguin_model2_coef <- tidy(model_2)
penguin_model2_coef
```
Try to write `r` code inline that spits our the coefficient for Gentoo. 

`r penguin_model2_coef$estimate[4]`


## Look at the model diagnostics: 

Use the plot() function. 

```{r}
plot(model_2)
```
## Report the model outputs in a summary table

USe modelsummary:
```{r}
modelsummary(model_2)


```

Use stargazer: 
```{r, results = "asis"}
stargazer(model_2, type = "html")
```

